% LaTeX resume using resume.cls
% !TeX program = lualatex
\documentclass[margin]{res}
\usepackage{fontspec}
\defaultfontfeatures{Mapping=tex-text}
\setromanfont[Mapping=tex-text]{Orkney}  \usepackage[activate={true,nocompatibility},final,tracking=true,factor=1100,stretch=10,shrink=10]{microtype}
\setlength{\textwidth}{5.1in} % set width of text portion

\begin{document}

% Center the name over the entire width of resume:
 \moveleft.5\hoffset\centerline{\large\bf Jason E. Parks}
% Draw a horizontal line the whole width of resume:
 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
 \moveleft.5\hoffset\centerline{email: jparks@jpconsulted.com}
 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
% address begins here
% Again, the address lines must be centered over entire width of resume:
 \moveleft.5\hoffset\centerline{215 NE 28th St Apt 3205 }
 \moveleft.5\hoffset\centerline{Oklahoma City, OK 73105}
 \moveleft.5\hoffset\centerline{(405) 604-7451}


\begin{resume}

\section{OBJECTIVE}  Jason Parks is an experienced Administrator of Red Hat, Debian, SuSE distributions of Linux, as well as Microsoft Windows. His Linux expertise includes:  Spacewalk/Red Hat Satellite 5, Katello/Red Hat Satellite 6, FreeIPA, Puppet, Ansible, and the scripting languages shell, Python, and Perl.  He also has extensive Dell PowerEdge server experience.  Jason has demonstrated his expertise by achieving the following vendor certifications:  Red Hat Certified Engineer, Novel Certified Linux Administrator, and Novell Data Center Technical Specialist.  Jason is currently looking for a Senior-level System Adminstrator or System Architect position. 

\section{COMPUTER \\ SKILLS}
	{\sl Languages \& Software:} Openshift Container Platform, Jenkins, Workato  \\
	{\sl Operating Systems:} Microsoft Windows, Red Hat Enterprise Linux, Debian Linux, SuSE Linux, Solaris and IBM AIX \\
	{\sl Open Source Projects:} Advanced: Puppet, Spacewalk, Katello, Pulp, Beginner: Redis, Elasticsearch, Logstash, Openstack \\
	{\sl Cloud Providers:} Linode, Google Compute, Amazon Web Services \\

\section{EXPERIENCE}
	{\sl Site Reliability Engineer} \hfill July 2022 - present \\
	Halo Diagnostics (Robert Half Technology)
	\begin{itemize} \itemsep -2pt 
		\item Develop solutions to various challenges to components of platform, related to deployment, monitoring and production operations
		\item Worked with Infrastructure team to ensure systems are optimal
		\item Implements and improves monitoring and alerting systems and SIEM to ensure environment is healthy and secure
		\item Logs, coordinates and resolves environment defects.
	\end{itemize}
	{\sl DevOps Engineer} \hfill January 2020 - July 2022 \\
	CompSource Mutual Insurance Company
	\begin{itemize} \itemsep -2pt 
		\item Manages and maintains Openshift Container Platform
		\item Responsible for creating and updating devops pipelines in Jenkins for CI/CD of applications
		\item Implements and improves monitoring and alerting by identifying measures or indicators of system performance and the actions needed to improve or correct performance, relative to the goals of the system.
		\item Performs test environment configuration, deployment and test activities required to provide a stable test platform.
		\item Tracks releases, upgrades and changes to the development and test environments.
		\item Logs, coordinates and resolves environment defects.
	\end{itemize}
	\clearpage
	{\sl Senior Systems Engineer} \hfill July 2017 - January 2020 \\
	Integris Health Inc
	\begin{itemize}  \itemsep -2pt %reduce space between items
		\item Provides highly responsive support to IT teams and hospitals around the state, troubleshoots complex L2/L3 issues
		\item Microsoft Azure Admin, managed migration from classic to ARM resources for the entire software stack, continues to apply best practices in cloud computing
		\item Main tasks include support of Linux servers, SELinux adoption, systems management, provisioning of new systems and software fixes
		\item Deployed Red Hat Identity Management for Active Directory authentication in Linux and AIX
		\item Maintains Ansible and Puppet code in git repositories. Documents all procedures and services
	\end{itemize}
	{\sl Committee Member} \hfill May 2014 - Present \\
    The Linux Foundation Item Writing Committee - LFCE Program
    \begin{itemize}  \itemsep -2pt %reduce space between items
	    \item Insuring the alignment of exam content with the the exam content blueprint.
	    \item Creating and approving certification exam questions and recommending an exam cut score.
	    \item Approving the equivalence of exam forms.
	    \item Annually reviewing item and exam performance and revising exam items to meet psychometric requirements.
	    \item Unable to hold either Certification within three years of exam launch as a result of serving as an item writer.
    \end{itemize}
	{\sl System Administrator} \hfill July 2013 - July 2017 \\
	Seagate Technology
	\begin{itemize}  \itemsep -2pt %reduce space between items
		\item Provides highly responsive support to local IT teams
		\item Main tasks include support of Unix servers and operating systems, systems management, provisioning of new systems, hardware repairs and software fixes
		\item Deployed Red Hat Satellite 6 for systems lifecycle management. Brought patching infrastructure up to date. Utilizes ITIL standards
		\item Deployed and manages Red Hat Identity Management (FreeIPA) for all unix systems
		\item Deployed Red Hat Enterprise Virtualization cluster to provide lower cost alternative to vmware virtualization.
		\item Manages Red Hat Enterprise Linux subscriptions and licensing.
		\item Deployed Openstack Kilo environment for development testing.
		\item Maintains code in git repositories.
	\end{itemize}
\end{resume}
\end{document}




